---
title: "MET tutorial code"
output: html_document
date created: "2023-04-11"
author: "Kelley Gunther"
update: "2023-05-26 by Xiaoxue Fu"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## adjust path to point to data
## .csv should be long-form data with ID, time variable (e.g. seconds), and columns with proportion of gaze to AOI per unit of time 
## Choose the directory containing df_dwell_all.csv
```{r}
#Install packages
list.of.packages <- c("tidyverse", "nlme")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)

#Set up input and output directories
path=choose.dir()
setwd(path)
fig.outpath <- paste0(getwd(), "/plots/")
if(!file.exists(fig.outpath)){
  dir.create(file.path(fig.outpath))
}

data <- read.csv("df_dwell_all.csv", header = TRUE)
```

## creating time squared variable for quadratic model fit
```{r}
data$timesq <- data$time^2
```

## fitting quadratic model - mask on
```{r}
stranger_mask_on_head_quad <- lme(strangerhead_prop_maskon ~ 1 + time + timesq,
                 random = ~ 1 + time + timesq | id,
                 data = data,
                 na.action = "na.exclude")

summary(stranger_mask_on_head_quad)
```

## quadratic model graph - mask on
```{r}
#obtaining predicted scores for individuals
data$pred_maskon <- predict(stranger_mask_on_head_quad)

#obtaining predicted scores for prototype
data$proto_maskon <- predict(stranger_mask_on_head_quad, level=0)

#plotting predicted trajectories
#intraindividual change trajetories
fig1 <- ggplot(data = data, aes(x = time, y = pred_maskon, group = id)) +
  #geom_point(color="black") + 
  geom_line(color="black") +
  geom_line(aes(x = time, y = proto_maskon), color="red",size=2) + 
  theme_classic() +
  xlab("Time (seconds)") + 
  ylab("Proportion of gaze") + ylim(0,1) +
  scale_x_continuous(breaks=seq(0,80,by=5)) +
  theme(axis.text=element_text(size=14), axis.title=element_text(size=18,face="bold"))
fig1

outname <- paste0(fig.outpath,"fig6a_MaskOn.tiff")
ggsave(outname, height = 6, width = 8)

```

## fitting quadratic model - mask off
```{r}
stranger_mask_off_head_quad <- lme(strangerhead_prop_maskoff ~ 1 + time + timesq,
                 random = ~ 1 + time + timesq | id,
                 data = data,
                 na.action = "na.exclude")

summary(stranger_mask_off_head_quad)
```

## quadratic model graph - mask off, attention to entire stranger head
```{r}
#obtaining predicted scores for individuals
data$pred_maskoff <- predict(stranger_mask_off_head_quad)

#obtaining predicted scores for prototype
data$proto_maskoff <- predict(stranger_mask_off_head_quad, level=0)

#plotting predicted trajectories
#intraindividual change trajetories
fig2 <- ggplot(data = data, aes(x = time, y = pred_maskoff, group = id)) +
  #geom_point(color="black") + 
  geom_line(color="black") +
  geom_line(aes(x = time, y = proto_maskoff), color="red",size=2) + 
  theme_classic() +
  xlab("Time (seconds)") + 
  ylab("Proportion of gaze") + ylim(0,1) +
  scale_x_continuous(breaks=seq(0,75,by=5)) +
  theme(axis.text=element_text(size=14), axis.title=element_text(size=18,face="bold"))
fig2

outname <- paste0(fig.outpath,"fig6b_MaskOff.tiff")
ggsave(outname, height = 6, width = 8)

```
